\begin{thebibliography}{99}

\bibitem{AkiRi2002} Aki, K. \& Richards, P. G., 2002. \emph{Quantitative
Seismology, 2nd edition}, University Science Books.

\bibitem{Babuska01} Babuska, V., Cara, M., 1991. \emph{Seismic anisotropy in the Earth}, Kluwer Acad. Pub.

\bibitem{Berenger} B\'{e}renger, J.-P., 1994. \emph{A perfectly matched layer
for the absorption of electromagnetic waves}, J. Comp. Phys.,
\textbf{114}, 185-200.

\bibitem{Blanch01} Blanch, J. O., Robertsson, J. O. A., Symes, W. W., 1995. \emph{Modelling of a constant Q: Methodology and algorithm for an efficient and optimally inexpensive viscoelastic technique}, Geophysics, \textbf{60}(1), 176-184.

\bibitem{Capdeville2007} Capdeville, Y., Marigo, J.-J., 2007.
Second order homogenization of the elastic wave equation for
non-periodic layered media, \emph{Geophys. J. Int.}, \textbf{170},
823-838.

\bibitem{Capdeville2008} Capdeville, Y., Marigo, J.-J., 2008.
\emph{Shallow layer correction for spectral element like methods},
Geophys. J. Int., \textbf{172}, 1135-1150.

\bibitem{Cerjan1985} Cerjan, C., Kosloff, D., Kosloff, R., Reshef,
M., 1985. \emph{A non reflecting boundary condition for discrete
acoustic and elastic wave calculations}, Geophysics, \textbf{50},
705-708.

\bibitem{ClayEngq} Clayton, R. \& Engquist, B., 1977.
\emph{Absorbing boundary conditions for acoustic and elastic wave
equations}, Bull. Seis. Soc. Am., \textbf{67}(6), 1529-1540.

\bibitem{Collino} Collino, F. \& Tsogka, C., 2001. \emph{Application
of the perfectly matched absorbing layer model to the linear
elastodynamic problem in anisotropic heterogeneous media},
Geophysics, \textbf{66}(1), 294-307.

\bibitem{DahlenTromp} Dahlen, F. A., Tromp, J., 1998.
\emph{Theoretical global seismology}, Princeton University Press.

\bibitem{Durek1996} Durek, J. J. \& Ekstro\"{o}m, G., 1996. \emph{A radial model of anelasticity consistent with long-period surface-wave attenuation}, Bull. Seis. Soc. Am., \textbf{86}, 144-158.

\bibitem{Dziewonski_PREM} Dziewonski, A. M., Anderson, D. L., 1981.
\emph{Preliminary reference Earth model}, Phys. Earth Planet. Int.,
\textbf{25}, 297-356.

\bibitem{FestaVilotte} Festa, G. \& Vilotte, J.-P., 2005. \emph{The
Newmark scheme as velocity-stress time-staggering: an efficient PML
implementation for spectral element simulations for elastodynamics},
Geophys. J. Int, \textbf{161}, 789-812.

\bibitem{FichtnerIgel2008} Fichtner, A., Igel, H., 2008. \emph{Efficient numerical surface wave propagation through the
optimization of discrete crustal models - a technique based on
non-linear dispersion curve matching (DCM)}, Geophys. J. Int.,
\textbf{173}(2), 519-533.

\bibitem{Fichtner2013a} Fichtner, A., Saygin, E., Taymaz, T., Cupillard, P., Capdeville, Y., Trampert, J., 2013a. \emph{The deep structure of the North Anatolian Fault zone}, Earth Planet. Sci. Lett., \textbf{373}, 109-117.

\bibitem{Fichtner2013b} Fichtner, A., Trampert, J., Cupillard, P., Saygin, E., Taymaz, T., Capdeville, Y., Villasenor, A., 2013b. \emph{Multi-scale full waveform inversion}, Geophys. J. Int., \textbf{194}, 534-556.

\bibitem{Kennett_1995} Kennett, B. L. N., Engdahl, E. R., Buland, R., 1995. \emph{Constraints on seismic velocities in the Earth from traveltimes}, Geophys. J. Int., 122, 108-124.

\bibitem{Kennett_elastic_wavefield2001} Kennett, B. L. N., 2001.
\emph{The seismic wavefield: Volume 1. Introduction and theoretical
development}, Cambridge University Press.

\bibitem{KomTrom03} Komatitsch, D. \& Tromp, J., 2003. \emph{A
perfectly matched layer absorbing boundary condition for the
second-order seismic wave equation}, Geophys. J. Int., \textbf{154},
146-153.

\bibitem{Love1892} Love, A. E. H., 1892. \emph{The mathematical theory of elasticity}, Cambridge Univ. Press.

\bibitem{Moczo2005} Moczo, P. \& Kristek, J., 2005. \emph{On the rheological methods
used for the time-domain methods of seismic wave propagation},
Geophys. Res. Lett., \textbf{32}(1), Art. No. L01306.

\bibitem{Ritsema2011} Ritsema, J., van Heijst, H. J., Deuss, A., Woodhouse, J. H., 2010. \emph{S40RTS: a degree-40 shear-velocity model of the mantle from new Rayleigh wave dispersion, teleseismic traveltimes, and normal-mode splitting function measurements}, Geophys. J. Int., \textbf{184},  doi:10.1111/j.1365–246X.2010.04884.x.

\bibitem{RobBlaSy1994} Robertsson, J. O. A., Blanch, J. O., Symes, W.
W., 1994. \emph{Viscoelastic finite-difference modeling},
Geophysics, \textbf{59}(9), 1444-1456.

\bibitem{Stacey} Stacey, R., 1988. \emph{Improved transparent
boundary formulations for the elastic-wave equation}, Bull. Seis.
Soc. Am., \textbf{78}(6), 2089-2097.

\bibitem{TakeuchiSaito} Takeuchi, H., Saito, M., 1972. \emph{Seismic
surface waves}, in \emph{Methods in Computational Physics, Vol. 11},
217-295, Academic Press.

\bibitem{Teixeira} Teixeira, F. L. \& Chew, W. C., 1997.
\emph{Systematic derivation of anisotropic pml absorbing media in
cylindrical and spherical coordinates}, IEEE Microwave and Guided
Wave Letters, \textbf{7}(11), 371-373.

\bibitem{Zheng} Zheng, Y. \& Huang, X., 2002. \emph{Anisotropic
perfectly matched layers for elastic waves in cartesian and
curvilinear coordinates}, MIT Earth Resources Laboratory, Consortium
Report.

\end{thebibliography}
